Stock enhancement undermines community stability

### 2022-01-31 rmd/manuscript.Rmd
edit: manuscript

## ssm estimate
df_bp <- list.files(path = here::here("data_fmt"), full.names = T) %>% 
  as_tibble() %>% 
  filter(str_detect(string = .$value, pattern = "ssm")) %>% 
  pull() %>% 
  lapply(function(x) {
    read_csv(x) %>% 
      filter(param == "bp_value") %>% 
      select(mean) %>% 
      mutate(group = str_extract(x, "all|masu|other"))
  }) %>% 
  bind_rows()

@@

Human demands for natural resources are ever increasing, such that active interventions are critical to the sustainable management of fisheries, forestry, and wildlife [@cardinaleBiodiversityLossIts2012]. Captive breeding is a common practice to enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996]. Although there is growing recognition that stock enhancement with captive-bred organisms entails ecological risks (e.g., the accumulation of deleterious alleles) [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996; @griffithsCaptiveBreedingReintroduction2008; @haagNorthAmericanFreshwater2012] and natural resource management [@kitadaEconomicEcologicalGenetic2018; @arakiHatcheryStockingHelp2010]. In fisheries for example, billions of hatchery-reared individuals are released annually across the globe [@kitadaEconomicEcologicalGenetic2018]. The widespread use of captive breeding is perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks.

Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of stock enhancement. Species are all embedded in the complex web of interacting organisms, and stable coexistence of competing species through density-dependent feedback underpins emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999a; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004]. Stock enhancement may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@weberInteractionsHatcheryWild2003; @careyNativeInvadersChallenges2012]. Hence, this form of species management may undermine the ecological process that allows competing species to coexist, ultimately compromising the long-term community stability. Evidence for this hypothesis is lacking, however.

Here, we use a simple theory to show that stock enhancement undermines long-term community stability, which we define here as the relative size of fluctuations in total community density over time [@tilmanEcologicalConsequencesChanges1999a]. Our theory illuminates that stock enhancement interferes with the internal regulation process of self-sustainable communities, compromising the stabilizing mechanism emerging from species niche differences. The present study further demonstrates the relevance of this general theory to natural systems by showing its congruence with Japanese stream fish communities, where \>10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes [@kitadaLessonsJapanMarine2020].

We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012] to simulate community dynamics with selective stock enhancement of a constituent species (species 1). Specifically, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:

@@

$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. Therefore, the model accounts for fitness difference of captive-bred individuals due to genetic effects and/or plasticity [@weberInteractionsHatcheryWild2003; @snyderLimitationsCaptiveBreeding1996; @arakiHatcheryStockingHelp2010] when considering the reproductive contribution of released individuals to the next generation of the enhanced species. Without loss of generality, we assumed constant $K_i$ ($K_i = K$) and $R_t$ ($R_t = R$) across species and time, respectively.

In our simulation, we considered `r nrow(param_set)` simulation scenarios with different values of the following ecological parameters: intrinsic growth of the enhanced species ($r_1=$ `r unique(sim_result$r1)`), average strength of interspecific competition ($\bar{\alpha}=$ `r unique(sim_result$alpha)`), carrying capacity ($K=$ `r unique(sim_result$k)`), degree of environmental stochasticity ($\sigma_{\epsilon}=$ `r unique(sim_result$sd_env)`), and relative fitness of captive-bred individuals ($f_R=$ `r unique(sim_result$phi)`). We chose these parameters because our sensitivity analysis revealed that they were influential in altering the relationship between community dynamics and stock enhancement (**Supporting Information**). Under each scenario with a unique parameter combination, we ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) with varying numbers of released individuals $R$ ($0-500$). The last `r unique(sim_result$n_timestep)` time steps were used to obtain the following summary statistics of total community density $\sum_i^SN_i$: the coefficient of variation (CV), the number of species persist (defined as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the temporal SD ($\sigma$). In addition, the temporal mean and SD were also calculated for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer mechanisms that underlie the community-level response.

When carrying capacity is small ($K=100$), our model predicted a destabilizing effect of selective stock enhancement on ecological communities as illustrated by increased CV with increasing numbers of released individuals $R$ (**Figure 1A**). This pattern stemmed mainly from the reduced mean of total community density, and both enhanced and unenhanced species groups were responsible (**Figure 1A**). For enhanced species, released individuals induced overcompensation, in which the negative effect of reduced per-capita reproduction due to competition exceeds the numerical benefit of released individuals. Therefore, the enhanced species reached the lower long-term average of population density with higher numbers of released individuals, confirming previous theoretical predictions [@satakeStockingCaptivebredFish2012]. Meanwhile, interspecific competition caused the reduced mean density of unenhanced species and led to decreased numbers of persisting species at high levels of stock enhancement (**Figure 1A**). Combined, the long-term average of the total community density decreased more sharply than individual species groups with stock enhancement (**Figure 1A**). The SDs showed a similar trend, but the relationship was flatter at the community level (**Figure 1A**). Since a CV is a ratio of an SD to a mean, the steeper relationship of the mean community density resulted in the increased CV. These patterns were qualitatively similar across most ecological scenarios even when interspecific competition is very weak (**Figure S1-6**).

The destabilizing effect emerges because stock enhancement undermines the balance of species interactions that underpins community stability. Ecological theory suggests that stable coexistence of competing species requires a niche difference that is large enough to overcome the relative difference in intrinsic competitive ability [@carrollNicheFitnessDifferences2011a]. Under this condition, competing species can grow from small populations because numerically dominant species undergoes stronger intraspecific competition [@carrollNicheFitnessDifferences2011a]. Such stable coexistence increases the likelihood of stabilizing temporal dynamics of species rich communities [@tilmanEcologicalConsequencesChanges1999a] because it gives rise to "overyielding" [@loreauDoesFunctionalRedundancy2004; @carrollNicheFitnessDifferences2011a], that is, total community density of a multi-species community exceeds what would be expected in a single species community ($\sum_i^S N_i > K$). However, stock enhancement is externally controlled and the number of release is not subject to density-dependent regulation. Therefore, excessive individuals supplemented through stock enhancement impose additional intra- and interspecific competition that interferes with the ecological process producing overyielding.

The only scenario where stock enhancement had little influence on community dynamics was when carrying capacity was sufficiently large ($K=500$; **Figures S7-S12**). In particular, stock enhancement increased the average density of the enhanced species with low population growth rate ($r_1=0.5$; **Figures S7 and S8**). This result may explain why some of the best evidence for successful stock enhancement comes from endangered species that typically suffer from increased mortality [@johnsonGeneticRestorationFlorida2010; @oppelPopulationReinforcementDemographic2021]. More importantly, the contrasting community response at different levels of carrying capacity casts light on the limitation of stock enhancement. One of the core motivations for stock enhancement is to mitigate or reverse declining trends of biodiversity due to human impacts, such as habitat loss and fragmentation [@chaseEcosystemDecayExacerbates2020]. Ironically, however, our results suggest that stock enhancement will not bring desired ecological outcomes unless we resolve root causes that compromise environmental capacity first.

To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of selective stock enhancement of masu salmon *Oncorhynchus masou masou* (**Figure 1E**) on the long-term stability of stream fish communities. Masu salmon is one of the most valuable freshwater resources in Hokkaido Island, Japan, and extensive hatchery programs have been implemented [@kitadaLessonsJapanMarine2020]. In protected watersheds (**Figure 1C and 1D**), long-term monitoring has been conducted over the past two decades along with official records of stock enhancement [@teruiMetapopulationStabilityBranching2018]. Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions. In this study, we used the long-term data (1999-2019) of stream fish communities at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see Methods for selection criteria). Using hierarchical Bayesian models, we quantified the effect of stock enhancement on community dynamics while accounting for potential confounding effects of climates and local abiotic factors.

As our theory predicts, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with greater numbers of fish released (**Figure 1B**). The positive relationship between the CV and the number of fish released was strongly supported by the statistical model (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S8**). This pattern was associated with the reduced long-term average of total community density and fewer species richness (**Figure 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figure 1B and 2;** see **Tables S8-S10** for full statistics). In the meantime, the SDs had vague relationships with stock enhancement, and neither positive nor negative relationship was supported by statistical analysis (**Figure 1B and 2**). At the population level, similar responses to stock enhancement have been reported in other fish and aquatic invertebrates [@arakiHatcheryStockingHelp2010]. Our analysis builds upon these findings by illustrating the community-level response.

In our theory, the observed pattern emerges when negative density dependence operates in the recipient community, and previous observations confirm this assumption. Masu salmon typically spend one year in freshwater before migrating to the ocean, and a wealth of evidence suggests that released masu salmon compete with wild masu salmon [@sahashiEvaluationContributionHatchery2015a] and other stream fishes [@hasegawaEffectsHatcheryChum2014; @hasegawaWildMasuSalmon2018]. Hatchery-reared salmons are larger and more aggressive than wild individuals, further increasing the likelihood of intense intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @weberInteractionsHatcheryWild2003]. Importantly, the number of fish released is controlled by socioeconomic factors (e.g., budget allocation). As such, released fish are "excessive" given the density-dependent regulation of recipient communities and may cause resource competition that would otherwise not exist.

Reduced fitness of captive-bred individuals may also play a role in producing the observed community response. As with other salmonid species, ocean-migrating adults of captive-bred masu salmon show lower return rates to the spawning river. It has also been shown that hatchery-reared salmons are more susceptible to predation than wild salmons [@weberInteractionsHatcheryWild2003]. The fitness disadvantage of captive-bred fish may add to negative density dependence to reduce the long-term average of community density, undermining community stability in the long term.

Like any non-experimental studies, we cannot exclude the possibility that our results were driven by spurious correlations. However, in the protected watersheds, any exploitation of aquatic species and alteration of in-stream habitats (e.g., construction of river-crossing structure) are strictly regulated; therefore, it is difficult to envision that unmeasured human influences played a major role in the observed relationships. Further, we have statistically controlled natural variation in environmental factors, including climatic and land use variables (see **Methods** and **Tables S8-S10**). This unique study setup may have helped uncover the close agreement between theory and empirical patterns.

The past few decades have witnessed substantial efforts to unveil ecological consequences of captive breeding, and there is a general agreement that the distinctive features of captive-bred individuals bring fitness disadvantages in the wild [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996]. As such, numerous studies suggested that stock enhancement with captive breeding must be carefully employed given the potential negative impacts on wild populations [@christieGeneticAdaptationCaptivity2012; @arakiGeneticEffectsCaptive2007]. Despite the significant attention to the fate of captive-bred individuals, current schemes rarely consider the self-regulation process of biodiversity. The results of this study suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community. While our empirical example is limited to stream fish communities, the consistent emergence of destabilizing effect across simulated ecological scenarios implies that this ecological phenomenon is pervasive across terrestrial and aquatic taxa.

We should prioritize the preservation and restoration efforts of natural habitats with a broader scope of biodiversity conservation. Such efforts are particularly important in the Anthropocene because the undesired influence of stock enhancement may be exacerbated in degraded habitats. Protected areas and environmental restoration are promising tools to conserve biodiversity, and the smart spatial design is key to achieve successful conservation [@koningNetworkGrassrootsReserves2020; @akasakaSmartProtectedArea2017]. For example, coordinated placement of conservation sites considering spatial biodiversity patterns is of critical importance in improving the ecological outcomes [@akasakaSmartProtectedArea2017; @teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020; @stollSmallImpoverishedRegional2013]. Socioeconomic factors such as governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018]. These considerable potentials indicate that we have viable management options for the sustainable future of natural resources before blindly accepting stock enhancement. Without a comprehensive framework that appreciates the ecological integrity of natural communities, stock enhancement will never be effective but impairs biodiversity.

>>>>

@@

Human demands for natural resources are ever-increasing, such that active interventions are critical to the sustainable management of fisheries, forestry, and wildlife [@laikreCompromisingGeneticDiversity2010]. Captive breeding is common to enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010]. Although there is growing recognition that releases of captive-bred organisms (hereafter, "stock enhancement") entail ecological risks (e.g., the accumulation of deleterious alleles) [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996] and natural resource management [@laikreCompromisingGeneticDiversity2010]. In fisheries, for example, billions of hatchery individuals are released annually across the globe [@kitadaEconomicEcologicalGenetic2018]. The widespread use of captive breeding is perhaps because of the "myth" that numerical benefits of released individuals may exceed the associated risks.

Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of stock enhancement. Species are all embedded in the complex web of interacting organisms, and the stable coexistence of competing species through density-dependent feedback underpins emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999a; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004]. Stock enhancement may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@weberInteractionsHatcheryWild2003; @careyNativeInvadersChallenges2012]. Hence, this form of species management may intervene in the ecological process that allows competing species to coexist, ultimately degrading the long-term community stability. Evidence for this hypothesis is lacking, however.

Here, we use a simple theory to show that stock enhancement undermines long-term community stability, which we define as the relative size of fluctuations in total community density over time [@tilmanEcologicalConsequencesChanges1999a]. Our theory illuminates that stock enhancement interferes with the internal regulation process of self-sustainable communities, compromising the stabilizing mechanism emerging from species niche differences. The present study further demonstrates the relevance of this general theory to natural systems by showing its congruence with Japanese stream fish communities, where \>10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes [@kitadaLessonsJapanMarine2020].

We employed a multispecies Ricker model [@fowlerSpeciesDynamicsAlter2012] to simulate community dynamics with the selective stock enhancement of a constituent species (species 1). Specifically, population density of species $i$ at time $t+1$, $N_{i,t+1}$, is modeled as:

@@

$f_R~(\ge 0)$ is the density-independent survival of captive-bred individuals relative to wild individuals. Therefore, the model accounts for the fitness difference of captive-bred individuals due to genetic effects and/or plasticity [@weberInteractionsHatcheryWild2003; @snyderLimitationsCaptiveBreeding1996; @arakiHatcheryStockingHelp2010] when considering the reproductive contribution of released individuals to the next generation. Without loss of generality, we assumed constant $K_i$ ($K_i = K$) and $R_t$ ($R_t = R$) across species and time, respectively. We ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) under each of `r nrow(param_set)` simulation scenarios that cover a range of ecological contexts (see **Materials and Methods**). The last `r unique(sim_result$n_timestep)` time steps were used to obtain the following summary statistics of the total community density $\sum_i^SN_i$: the coefficient of variation (CV), the number of species persist (defined as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the temporal SD ($\sigma$). We also calculated the temporal mean and SD for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer mechanisms that underlie the community-level response.

When carrying capacity is small ($K=100$), our model predicted a destabilizing effect of stock enhancement on ecological communities as illustrated by increased CV with increasing numbers of released individuals $R$ (**Figure 1A**). This pattern stemmed mainly from the reduced mean of total community density, and both enhanced and unenhanced species groups were responsible (**Figure 1A**). For enhanced species, released individuals induced overcompensation, in which the negative effect of reduced per-capita reproduction due to competition exceeds the numerical benefit of released individuals. Therefore, the enhanced species reached the lower long-term average of population density with stocking, confirming previous theoretical predictions [@satakeStockingCaptivebredFish2012]. Meanwhile, interspecific competition reduced the unenhanced species with fewer persisting species at high levels of stock enhancement (**Figure 1A**). Combined, the long-term average of the total community density decreased more sharply than individual species groups with stock enhancement (**Figure 1A**). The SDs showed a similar trend, but the relationship was flatter at the community level (**Figure 1A**). Since a CV is a ratio of an SD to a mean, the steeper relationship of the mean community density resulted in the increased CV. These patterns were qualitatively similar across most ecological scenarios (**Figure S1-6**).

The destabilizing effect emerges because stock enhancement affects the balance of species interactions that underpins community stability. In theory, the stable coexistence requires a niche difference that is large enough to overcome the relative difference in intrinsic competitive ability [@carrollNicheFitnessDifferences2011a]. Under this condition, competing species can grow from small populations because dominant species undergo stronger intraspecific competition [@carrollNicheFitnessDifferences2011a]. Such coexistence favors stable temporal dynamics of species-rich communities [@tilmanEcologicalConsequencesChanges1999a] because it gives rise to "overyielding" [@loreauDoesFunctionalRedundancy2004; @carrollNicheFitnessDifferences2011a], i.e., total community density of a multispecies community exceeds what would be expected in a single species community ($\sum_i^S N_i > K$). However, stock enhancement is externally controlled, and the number of releases is not subject to density-dependent regulation. Therefore, released individuals impose additional intra- and interspecific competition that interferes with the ecological process producing overyielding.

Stock enhancement, however, had little influence on community dynamics when carrying capacity was sufficiently large ($K=500$; **Figures S7-S12**). In particular, stock enhancement increased the enhanced species with a low population growth rate ($r_1=0.5$; **Figures S7 and S8**). This result may explain why some of the best evidence for successful stock enhancement comes from long-lived endangered species [@johnsonGeneticRestorationFlorida2010; @oppelPopulationReinforcementDemographic2021]. More importantly, the contrasting community response at different carrying capacities provides deeper insights. One of the core motivations for stock enhancement is to mitigate declining trends of natural resources due to human impacts, such as habitat loss and fragmentation [@chaseEcosystemDecayExacerbates2020]. Ironically, our results suggest that stock enhancement will not bring desired outcomes unless we resolve root causes that compromise environmental capacity first.

To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of selective stock enhancement of masu salmon *Oncorhynchus masou masou* (**Figure 1E**) on the long-term stability of stream fish communities in Hokkaido, Japan. Masu salmon is one of Japan's most valuable freshwater resources, and over 10 million hatchery fish are released annually across the nation [@kitadaLessonsJapanMarine2020]. In the protected watersheds (**Figure 1C and 1D**), the Hokkaido government led the standardized monitoring of fish communities over the past six decades, along with the official stocking records. Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions. In this study, we used the long-term community data (1999-2019) at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see Methods for selection criteria). Using hierarchical Bayesian models, we quantified the effect of stock enhancement on community dynamics while accounting for potential confounding effects of climates and local abiotic factors.

As predicted, stream fish communities showed greater temporal fluctuations (higher CV) in watersheds with greater numbers of fish released (**Figure 1B**). Our analysis strongly supports the positive relationship between the CV and the number of releases (**Figure 2**), in which the probability of the regression coefficient being positive was `r op(df_beta$all$prob_positive[df_beta$all$response == "cv"])` (**Table S8**). This pattern was associated with the reduced long-term average of total community density and fewer species richness (**Figure 1B and 2**), and both enhanced (masu salmon) and unenhanced fish groups contributed to this trend (**Figure 1B and 2;** see **Tables S8-S10** for full statistics). In the meantime, the SDs had vague relationships with stock enhancement (**Figure 1B and 2**).

Competition with wild masu salmon and other fish species is a likely mechanism, as our theory assumes. Field experiments confirmed that hatchery masu salmon competed with wild masu salmon and other stream fishes during their freshwater life stage, typically one year [@hasegawaEffectsHatcheryChum2014; @hasegawaWildMasuSalmon2018]. Hatchery salmons are larger and more aggressive than wild individuals, increasing the likelihood of intense intra- and interspecific competition in the wild [@hasegawaWildMasuSalmon2018; @weberInteractionsHatcheryWild2003]. Importantly, socioeconomic factors control the number of releases (e.g., budget allocation). As such, released fish are "excessive" given the density-dependent regulation of recipient communities and may cause resource competition that would otherwise not exist.

The reduced fitness of hatchery masu salmon may also play a role in the observed response. Like other salmonids, ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress]. Hatchery salmons are also more susceptible to predation than wild ones [@weberInteractionsHatcheryWild2003]. The fitness disadvantage of captive-bred fish may add to negative density dependence to influence community stability.

Like any non-experimental study, we cannot exclude the possibility that spurious correlations drove our results. However, in the protected watersheds, human activities (e.g., exploitation, construction of river-crossing structures) are strictly regulated; therefore, it is difficult to envision that unmeasured human influences caused the observed relationships. Further, we have statistically controlled natural variation in environmental factors, including climatic and land-use variables (see **Materials and Methods** and **Tables S8-S10**). This unique setup may have helped uncover the close agreement between theory and empirical patterns.

The past few decades have witnessed substantial efforts to unveil ecological consequences of captive breeding, and there is a general agreement that the distinctive features of captive-bred individuals bring fitness disadvantages in the wild [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996]. Despite the significant attention to the fate of captive-bred individuals, current schemes rarely consider the self-regulation process of biodiversity. Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community. While our empirical example is limited to stream fish communities, the destabilizing effect emerged across diverse simulated scenarios, implying that this phenomenon is pervasive across terrestrial and aquatic taxa.

We should prioritize habitat preservation and restoration with a broader scope of biodiversity conservation. Such efforts are particularly important in the Anthropocene because habitat degradation may exacerbate the undesired influence of stock enhancement. Protected areas and environmental restoration are promising tools to conserve biodiversity, and the smart spatial design is key to achieving successful conservation [@koningNetworkGrassrootsReserves2020; @akasakaSmartProtectedArea2017]. For example, coordinated placement of conservation sites considering spatial biodiversity patterns is crucial in improving the ecological outcomes [@akasakaSmartProtectedArea2017; @teruiEmergentDualScaling2021; @koningNetworkGrassrootsReserves2020]. Socioeconomic factors such as governance may also play a central role in enforcing environmental legislation, potentially determining the effectiveness of conservation investment [@amanoSuccessfulConservationGlobal2018]. These considerable potentials indicate that viable management options for the sustainable future exist before blindly accepting stock enhancement. Without a comprehensive framework that appreciates the ecological integrity of natural communities, the stock enhancement will never be effective but impairs biodiversity.
